Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-11-14 index.qmd
add Laurent's comments

```{r Plot Table Pigment}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: >
#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin; [@ralph2002 ; @Douay2022 @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
#| label: fig-Pigm
#| fig-width: 10
#| fig-height: 5
#| out-width: "100%"

>>>>

```{r Plot Table Pigment}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: >
#|   Photosynthetic and carotenoid pigments present (Green) or absent (Red) in each taxonomic class present in the Neural Network Classifier, along with their absorption wavelength measured with spectroradiometer, Chl-b: chlorophyll-b, Chl-c: chlorophyll-c, Fuco: fucoxanthin, Zea: zeaxanthin, Diad: diadinoxanthin, Lut: lutein, Neo: neoxanthin, PE: phycoerythrin, PC: phycocyanin; [@ralph2002 ; @Douay2022 ; @christensen1977seaweeds ; @cartaxana2016regulation ; @meleder2013vivo].
#| label: fig-Pigm
#| fig-width: 10
#| fig-height: 5
#| out-width: "100%"
